Compositional equivalences based on Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-12-06 2016-Weak-FH-Bisim/WeakBisim.tex
2 more TODOs done.

Fig. \ref{SimpleProt:Spec} (right) shows a graphical view of the pNet of the system \emph{specification}:
the full system should be equivalent (e.g. through weak bisimulation)
to the two processes connected simply through a perfect medium. \TODO{ 
The pNet has a tree-like structure.  The root node of the tree {\it SimpleSystemSpec} is the top level of the pNet structure. It acts
as the parallel operator. It consists of tree nodes: two Holes $P$ and $Q$ and one subnet, noted {\it PrefectMedium}. Nodes of the tree are synchronized using four synchronization vectors, that  express the possible synchronization between the parameterized actions of a subset of the nodes. For instance, in the vector "$< p\_send(m),in(m),\_> \rightarrow \underline{in(m)}$ both $P$ and {\it PrefectMedium} nodes are involved in the synchronization. In particular, this means the synchronization between these processes occurs when  process $P$  performs $p\_send(m)$  action sending a message, and  the medium accepts the message through $in(m)$ action  at the same time. And the result that will be returned at upper level is the internal action  $\underline{in(m)}$.
}

@@

The semantics of open pNets will be defined  as an open automaton. An open
automaton is an automaton where each transition composes transitions of several LTSs with
action of some holes, the transition occurs if some predicates hold, and can involve a 
set of state modifications. This section defines open automata and a bisimulation theory for them.
\TODO{Add initialisation of state vars}

@@

An open automaton is then simply an automaton where each transition is an open transition.
\begin{definition}[Open automaton]
	\label{def:open-automaton}
	An \emph{open automaton} is a structure\\ $A =
	<J,\mathcal{S},s_0,\mathcal{T}>$ where:
	\begin{itemize}
		\item[$\bullet$]   $J$ is a  set of indices,
		\item[$\bullet$]   $\mathcal{S}$ is a set of states and $s_0$ an initial state
		among $\mathcal{S}$,
		\item[$\bullet$] $\mathcal{T}$ is a set of open transitions and for each
		$t\in \mathcal{T}$ there exist  $J'$ with  $J'
		\subseteq J$, such that $t$ is an open transition over  $J'$
		and  $\mathcal{S}$.

@@

\TODO{Eric: rewrite example with new Protocolkeep only OT1, and adapt comments}
\begin{example}\emph{An open-transition.}
  \label{OT:ABP}
At the upper level, the $SimpleSystem$ pNet has 2 holes and $SimpleProtocol$ as
a subnet. One of its possible open transitions (synchronizing the hole $P$
with the $Sender$ within the \emph{SimpleProtocol}) is:

@@

    \smallskip
    The global states here have the same structure than
    in $OT_2$, as the holes have no states. The assignment
    $Post$ uses a variable from the action of hole $P$ to set the
    value of the sender state variable $s1\_m$.

@@

And here is a  drawing of this open automaton, slightly simplified for readability:

\begin{figure}[h]
  \centerline{\includegraphics[width=10cm]{ATG/SPImplOpen}}
  \caption{Open Automaton of the Simple Protocol Implementation}  \label{Annex:SimpleProtCounter:ImplOA}
\end{figure}

And a partially saturated Automaton:

\begin{figure}[h]
  \centerline{\includegraphics[width=13cm]{ATG/SPImplWeakOpen}}
  \caption{Weak Open Automaton, partial}  \label{SimpleProtCounter:ImplWOA}
\end{figure}

In Figure \ref{Annex:SimpleProtCounter:ImplWOA}, we have added some of the weak transitions generated by the saturation, namely:
- a tau-loop on each state
- a transition from <s0\_a0\_r0> to <s2\_a1\_r0>, resulting from the sequence OT\-1;OT\-6 followed by any number of the loop (OT\_9;ot\_12;OT\_6).

>>>>

Fig. \ref{SimpleProt:Spec} (right) shows a graphical view of the pNet of the system \emph{specification}:
the full system should be equivalent (e.g. through weak bisimulation)
to the two processes connected simply through a perfect medium. \RAB{ 
The pNet has a tree-like structure.  The root node of the tree {\it SimpleSystemSpec} is the top level of the pNet structure. It acts
as the parallel operator. It consists of tree nodes: two Holes $P$ and $Q$ and one subnet, noted {\it PrefectMedium}. Nodes of the tree are synchronized using four synchronization vectors, that  express the possible synchronization between the parameterized actions of a subset of the nodes. For instance, in the vector "$< p\_send(m),in(m),\_> \rightarrow \underline{in(m)}$ both $P$ and {\it PrefectMedium} nodes are involved in the synchronization. In particular, this means the synchronization between these processes occurs when  process $P$  performs $p\_send(m)$  action sending a message, and  the medium accepts the message through $in(m)$ action  at the same time. And the result that will be returned at upper level is the internal action  $\underline{in(m)}$.
}

@@

The semantics of open pNets will be defined  as an open automaton. An open
automaton is an automaton where each transition composes transitions of several LTSs with
action of some holes, the transition occurs if some predicates hold, and can involve a 
set of state modifications. This section defines open automata and a bisimulation theory for them.
\TODO{Add initialisation of state vars: done in Defn of OA}

@@

An open automaton is then simply an automaton where each transition is an open transition.
\begin{definition}[Open automaton]
	\label{def:open-automaton}
	An \emph{open automaton} is a structure\\ $A =
	<J,\mathcal{S},s_0,\mathcal{T}>$ where:
	\begin{itemize}
		\item[$\bullet$]   $J$ is a  set of indices,
		\item[$\bullet$]   $\mathcal{S}$ is a set of states and $s_0$ an initial state
		  among $\mathcal{S}$,
                  \item[$\bullet$] for each state $s$, $vars(s)=\{v_s\}$ is a set of state variables, and each $v_s$ may have an initial value $init(v_s)$.
		\item[$\bullet$] $\mathcal{T}$ is a set of open transitions and for each
		$t\in \mathcal{T}$ there exist  $J'$ with  $J'
		\subseteq J$, such that $t$ is an open transition over  $J'$
		and  $\mathcal{S}$.

@@

%\TODO{Eric: rewrite example with new Protocolkeep only OT1, and adapt comments}
\begin{example}\emph{An open-transition.}
  \label{OT:ABP}
At the upper level, the $SimpleSystem$ pNet has 2 holes and $SimpleProtocol$ as
a subnet, itself containing 3 pLTSs. One of its possible open transitions
(synchronizing the hole $P$
with the $Sender$ within the \emph{SimpleProtocol}) is:

@@

    \smallskip
    The global states here are triples, build as the product of states of the 3 pLTS (remember the Holes have no state). The assignment
    $Post$ uses a variable from the action of hole $P$ to set the
    value of the sender state variable $s1\_m$.
    \TODO{need more comments ?}

@@

%% And here is a  drawing of this open automaton, slightly simplified for readability:

%% \begin{figure}[h]
%%   \centerline{\includegraphics[width=10cm]{ATG/SPImplOpen}}
%%   \caption{Open Automaton of the Simple Protocol Implementation}  \label{Annex:SimpleProtCounter:ImplOA}
%% \end{figure}

%% And a partially saturated Automaton:

%% \begin{figure}[h]
%%   \centerline{\includegraphics[width=13cm]{ATG/SPImplWeakOpen}}
%%   \caption{Weak Open Automaton, partial}  \label{SimpleProtCounter:ImplWOA}
%% \end{figure}

%% In Figure \ref{Annex:SimpleProtCounter:ImplWOA}, we have added some of the weak transitions generated by the saturation, namely:
%% - a tau-loop on each state
%% - a transition from <s0\_a0\_r0> to <s2\_a1\_r0>, resulting from the sequence OT\-1;OT\-6 followed by any number of the loop (OT\_9;ot\_12;OT\_6).
